Beyond query expansion - expanding documents for fluid keyword search

### 2020-10-10 IUI2021/paper.tex
Grammarlyを通した

% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}

@@

People are frequently searching information using keywords on Google
and other systems.
But keyword search is still not an easy task,
because it is fundamentally difficulto to find appropriate information
that does not contain the keyword given by the user.

@@

We can get this kind of information fairly easily using Google and other search engines on the net,
so many people prefer getting information on the net rather than
using help systems provided by manufacturers.

We can find information on Google because there are tremendous information
that describe how to ``remove a file'' on Mac.
If there are documens that contain ``remove'', ``file'', and ``Mac'',
finding such documents are not difficult.
That seems to be the main reason why people are satisfied with search engines
for finding popular information.

@@

FAQs (frequently asked questions) by manufacturers and service providers are
usually not considered useful
because the words used in the documents are
often different from the keywords that user can imagine.

@@

Even finding the users' old memos can be sometimes difficult,
because people might use different keywords for the same thing case by case.
He might try to find a file related to ``IUI'' and fail, because he used
the term ``intelligent user interface'' for the file name.
%
Various techniques have been proposed to solve this vocabulary problem\cite{Furnas:1987:VPH:32206.32212},
but not very successful enough.

@@

Finding documents are even more difficult when
the user's mother language is different from the language used in the document.
When a user wants to find how to ``delete a file'' but the
manual of the system is written in French,
he has to \textit{translate} the term ``delete'' and ``file'' into French
before the search.
Non-English speakers are always having trouble
translating the word in their brain into English words
before searching information, because important information are
usually provided in English.

@@

The vocabulary problem and the translation problem can partially be solved
if the search system have a thesaurus and a translation dictionary.
%
For example, 
if the system knows that removing a file and deleting a file mean the same thing,
the system can try to find something using the keyword ``delete'',
even when the user specified the keyword ``remove''.
%
Techniques like this are called ``\textit{Query expansion}''\footnote{
  \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Query\_expansion}
},
and simple query expansion is effective if a good thesaurus is available.

@@

Query expansion is effective when simple substitution of keywords are satisfactory enough.
In the previous example, using the keyword ``delete'' in addition to ``remove'' works
for finding the manual entry.
More sophisticated query expansion techniques are widely used in various modern
information retrieval systems.

However, query expansion techniques do not work for finding a document for vague topics.
For example, if you want to find a document that describes ``how to write a good paper'',
you will have little chance finding a document related to the topic.
Maybe it would be better to use keywords like ``how to persuade reviewers''.
However, expanding a phrase like ``write a good paper'' to ``persude reviewers'' is impossible,
unless the expander understands the intension of the user.

@@

  When we want to publish a easy-to-find manual that describes how to delete a file,
  we expand the original document by
  providing REs like \qtt{(delete|remove) (a file|data)}
  and generating all the texts that match the REs.
  In this case, we can epand this RE into
  \qtt{delete a file},
  \qtt{delete data},
  \qtt{remove a file}, and
  \qtt{remove data},
  and use all these strings for the search.
  Users can find this document by using various query keywords like
  \qtt{delete}, \qtt{remove}, etc.
  We can add REs in other languages
  like \qtt{(ファイル|データ)を(消す|(消去|削除)する)}.
  A Japanese user can use a phrase like ``ファイルを消去する'' to find the manual page.

@@

  Since people frequently make spelling errors,
  approximate pattern matching algorithms
  work effectively for almost all search activities.
  After getting all the expresssions expanded by the {\ES} algorithm,
  simple approximate pattern matching algorithms work effectively.
  For example, a query string like \qtt{del dta} will work for
  finding a document that describes how to ``delete data''.

@@

In the next section, we describe how
document expansion strategy based on {\ES} works in various environments.

@@

Unix command line tools usually have many options and features that are difficult to
understand and remember.
For example, many programmers are recently using a version controll system
``git''\footnote{
  \ssf{https:{\slash}{\slash}git-scm.com{\slash}}
},
but the concept of git is difficult and the command line options are extremely complicated.
The total number of git manuals pages is bigger than 70,000.

@@

Figure \ref{paypayhf} shows an example {\HF} page that supports finding FAQs
for ``PayPay Free Market'' run by Yahoo! Japan\footnote{
  \ssf{https:{\slash}{\slash}paypayfleamarket.yahoo.co.jp{\slash}help{\slash}}
} and ``Siroca'', a consumer electronics company.

@@

After the introduction of ExpandSearch-based FAQ services,
the number of phone calls to the customer support center of these companies have
dropped to 40\%.
%
The ``hit rate'' at which users could find the information they need was 98\%.

@@

A flexible search mechanism ``{\ES}'' is used in {\HL}.
%
The database used in {\ES} are provided as a set of data entries
consisting of a regular expression that represents description of the data entry
and a corresponding command pattern string.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns represents the generated command string
corresponding to the description.
%
For example, a help entry for showing the difference between
current file and older file can be defined like this:

@@

Finding appropriate entries from the
% (possibly huge)
help document space is
performed in two steps.
First, a state transition diagram is generated from the regular expressions
used in the descriptions.
Second, all the description strings are generated by expanding the regular expression
into a tree, and filter the generated strings by the pattern specified by the user.
Efficient pattern matching is performed every time a new description text is generated,
and only the best-matched descriptions are shown to the user as menu entries.
We call this the ``\textit{generate-and-filter}'' technique,
and we will describe the details later.

@@

Using the state transition diagram shown in Figure \ref{statemachine1},
{\ES} generates all the strings represented in the regular expressions,
and filter them by the pattern provided by the user.

@@

``Generate-and-test''\footnote{
  {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
}
is a simple and effective strategy used for solving puzzles.
For example,
the ``8-Queen'' problem can be solved simply by
generating all the possible queen layouts and checking if
two or more queens are laid out on the same row, column, or diagonal line.
Although this strategy is simple, the cost of
generating all the possible solutions is prohibitive, since
the solution space of the 8-Queen puzzle is $8^8 = 16,777,216$,
which is not a small amount even for today's computers.

@@

On text editors and Unix shells,
``text completion'' feature has been available for a long time.
%
When a user types the TAB key after typing \sqtt{la} on the Unix shell,
\sqtt{latex}, \sqtt{last}, and other Unix commands are shown as candidates.
When a user types \sqtt{ls RE} and types the TAB key,
the shell checks the directory, find the \stt{README.md} file, and
replace the user's input with \sqtt{ls README.md}.
This behavior is called ``text completion'', and many variations of
this idea have been proposed and adopted in command shells and text editors.

@@

Gitsome\footnote{\textsf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}}
helps {\GIT} users by
dynamically showing possible arguments and related manuals on the Unix shell,
just like {\HL} does.
The goal of Gitsome is almost the same as {\HL} and we agree with its concept,
but Gitsome does not support flexible approximate matching and
help data sharing.

@@

We proposed the ``translation paradigm'' for bridging the gap between
users' intention and actual operations.
%
We have introduced a general-purpose flexible framework {\ES}
that can translate fragments of user's vague intentions into
concrete command strings required to control computers and
other complex artifacts.
We showed the principles and applications of {\ES} by using it
for {\HL}, a help system for supporting {\GIT} users
based on the shared database that any user can edit to share
translation knowledge between users.
%
{\ES} framework is useful for any kind of systems that need
some kind of user support, and we are planning to use it
for various applications and Web services in the future.

>>>>

@@

People are frequently searching for information using keywords on Google
and other systems.
But keyword search is still not an easy task because it is
fundamentally difficult to find appropriate information that does not
contain the user's keywords.

@@

We can get this kind of information fairly easily using Google and
other search engines on the net, so many people prefer getting
information on the net rather than using manufacturers' help systems.

We can find information on Google because there is tremendous information
that describes how to ``remove a file'' on Mac.
If there are documents that contain ``remove,'' ``file,'' and ``Mac'',
finding such documents are not difficult.
That seems to be the main reason why people are satisfied with search engines
for finding popular information.

@@

FAQs (frequently asked questions) by manufacturers and service providers are
usually not considered useful
because the words used in the documents are
often different from the keywords that users can imagine.

@@

Even finding the users' old memos can be sometimes difficult,
because people might use different keywords for the same thing case by case.
He might try to find a file related to ``IUI'' and fail because he used
the term ``intelligent user interface'' for the file name.
%
Various techniques have been proposed to solve this vocabulary problem\cite{Furnas:1987:VPH:32206.32212},
but not very successful enough.

@@

Finding documents is even more difficult when
the user's mother language is different from the language used in the document.
When a user wants to find how to ``delete a file'' but the
manual of the system is written in French,
he has to \textit{translate} the term ``delete'' and ``file'' into French
before the search.
Non-English speakers are always having trouble
translating the word in their brains into English words
before searching for information, because important information is
provided in English in many cases.

@@

The vocabulary problem and the translation problem can partially be solved
if the search system has a thesaurus and a translation dictionary.
%
For example, 
if the system knows that removing a file and deleting a file means the same thing,
the system can try to find something using the keyword ``delete''
even when the user specified the keyword ``remove.''
%
Techniques like this are called ``\textit{Query expansion}''\footnote{
  \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Query\_expansion}
},
and simple query expansion is effective if a good thesaurus is available.

@@

Query expansion is effective when a simple substitution of keywords is satisfactory enough.
In the previous example, using the keyword ``delete'' in addition to ``remove'' works
for finding the manual entry.
More sophisticated query expansion techniques are widely used in various modern
information retrieval systems.

However, query expansion techniques do not work for finding a document for vague topics.
For example, if you want to find a document that describes ``how to write a good paper,''
you will have little chance of finding a document related to the topic.
Maybe it would be better to use keywords like ``how to persuade reviewers.''
However, expanding a phrase like ``write a good paper'' to ``persuade reviewers'' is impossible,
unless the expander understands the intention of the user.

@@

  When we want to publish an easy-to-find manual that describes how to delete a file,
  we expand the original document by
  providing REs like \qtt{(delete|remove) (a file|data)}
  and generating all the texts that match the REs.
  In this case, we can expand this RE into
  \qtt{delete a file},
  \qtt{delete data},
  \qtt{remove a file}, and
  \qtt{remove data},
  and use all these strings for the search.
  Users can find this document by using various query keywords like
  \qtt{delete}, \qtt{remove}, etc.
  We can add REs in other languages
  like \qtt{(ファイル|データ)を(消す|(消去|削除)する)}.
  A Japanese user can use a phrase like ``ファイルを消去する'' to find the manual page.

@@

  Since people frequently make spelling errors,
  approximate pattern matching algorithms
  work effectively for almost all search activities.
  After getting all the expressions expanded by the {\ES} algorithm,
  simple approximate pattern matching algorithms work effectively.
  For example, a query string like \qtt{del dta} will work for
  finding a document that describes how to ``delete data.''

@@

In the next section, we describe how
document-expansion strategy based on {\ES} works in various environments.

@@

Unix command-line tools usually have many options and features that are difficult to
understand and remember.
For example, many programmers are recently using a version control system
``git''\footnote{
  \ssf{https:{\slash}{\slash}git-scm.com{\slash}}
},
but the concept of git is difficult, and the command-line options are extremely complicated.
The total number of git manuals pages is bigger than 70,000.

@@

Figure \ref{paypayhf} shows an example {\HF} page that supports finding FAQs
for ``PayPay Free Market''\footnote{
  \ssf{https:{\slash}{\slash}paypayfleamarket.yahoo.co.jp{\slash}help{\slash}}
} run by Yahoo! Japan and ``Siroca''\footnote{
  \ssf{https:{\slash}{\slash}www.siroca.co.jp{\slash}support{\slash}}
}, a consumer electronics company.

@@

After introducing ExpandSearch-based FAQ services,
the number of phone calls to the customer support center of these companies has
dropped to 40\%.
%
The ``hit rate'' at which users could find the information they need was 98\%.

@@

A flexible search mechanism, ``{\ES}'', is used in {\HL}.
%
The database used in {\ES} is provided as a set of data entries
consisting of a regular expression that represents a description of the data entry
and a corresponding command pattern string.
A description string is used to produce natural language texts
easily understandable by users,
while command patterns represent the generated command string
corresponding to the description.
%
For example, a help entry for showing the difference between
current file and older file can be defined like this:

@@

Finding appropriate entries from the
% (possibly huge)
help document space is
performed in two steps.
First, a state transition diagram is generated from the regular expressions
used in the descriptions.
Second, all the description strings are generated by expanding the regular expression
into a tree, and filtering the generated strings by the user's pattern.
Efficient pattern matching is performed every time a new description text is generated,
and only the best-matched descriptions are shown to the user as menu entries.
We call this the ``\textit{generate-and-filter}'' technique,
and we will describe the details later.

@@

Using the state transition diagram shown in Figure \ref{statemachine1},
{\ES} generates all the strings represented in the regular expressions
and filter them by the pattern provided by the user.

@@

``Generate-and-test''\footnote{
  \ssf{http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
}
is a simple and effective strategy used for solving puzzles.
For example,
the ``8-Queen'' problem can be solved simply by
generating all the possible queen layouts and checking if
two or more queens are laid out on the same row, column, or diagonal line.
Although this strategy is simple, the cost of
generating all the possible solutions is prohibitive, since
the solution space of the 8-Queen puzzle is $8^8 = 16,777,216$,
which is not a small amount even for today's computers.

@@

On text editors and Unix shells,
``text completion'' has been available for a long time.
%
When a user types the TAB key after typing \sqtt{la} on the Unix shell,
\sqtt{latex}, \sqtt{last}, and other Unix commands are shown as candidates.
When a user types \sqtt{ls RE} and types the TAB key,
the shell checks the directory, find the \stt{README.md} file, and
replace the user's input with \sqtt{ls README.md}.
This behavior is called ``text completion'', and many variations of
this idea have been proposed and adopted in command shells and text editors.

@@

Gitsome\footnote{
  \ssf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}
} helps {\GIT} users by
dynamically showing possible arguments and related manuals on the Unix shell,
just like {\HL} does.
The goal of Gitsome is almost the same as {\HL} and we agree with its concept,
but Gitsome does not support flexible approximate matching and
help data sharing.

@@

We proposed the ``document expansion'' paradigm for
flexible text search and
the ``translation paradigm'' for bridging the gap between
users' intention and actual operations.
%
We have introduced a general-purpose flexible framework, {\ES},
that can translate fragments of user's vague intentions into
concrete strings required to search for information or
control computers and other complex artifacts.
We showed the principles and applications of {\ES} by using it
for {\HL}, a help system for supporting command-line users
based on the shared database that any user can edit to share
translation knowledge between users.
%
{\ES} framework is useful for any systems that need
some user support, and we are planning to use it
for a wider range of applications and Web services in the future.
